---
title: "Final Project Report"
author: "Anyue Ruan"
date: "`r Sys.Date()`"
output: html_document
---

#Introduction

The data is about smoking and lung cancer status. It includes people of different age groups, different genders and whether they have lung cancer or not. And, the data set also includes different information such as anxiety level, severity of smoking, and even peer pressure.
The data is collected from the website online lung cancer prediction system .
Gender: M(male), F(female)
Age: Age of the patient
Smoking: YES=2 , NO=1.
Yellow fingers: YES=2 , NO=1.
Anxiety: YES=2 , NO=1.
Peer_pressure: YES=2 , NO=1.
Chronic Disease: YES=2 , NO=1.
Fatigue: YES=2 , NO=1.
Allergy: YES=2 , NO=1.
Wheezing: YES=2 , NO=1.
Alcohol: YES=2 , NO=1.
Coughing: YES=2 , NO=1.
Shortness of Breath: YES=2 , NO=1.
Swallowing Difficulty: YES=2 , NO=1.
Chest pain: YES=2 , NO=1.
Lung Cancer: YES , NO.


#Loading data

```{r, load-data}
here::i_am("report.Rmd")
data <- readRDS(
  file = here::here("output/cleaned_data.rds")
)

```

#Output

According to the analysis, the age of the target patients skewed to the left. The proportion of older patients is significantly larger. Majority of patients have the habbit of smoking, causing yellow fingers. Among all variables, fatigue has the biggest differences. Almost all patients have problems of feeling exhausted. 

```{r, description, echo = FALSE, message = FALSE}
basic<-readRDS(here::here("output/Table_Basic.rds"))
basic
```

```{r, agedistribution, echo = FALSE, message = FALSE}
knitr::include_graphics(
  here::here("output/Age_Distribution.png")
)
```

```{r, table, echo = FALSE, message = FALSE}
plot<-readRDS(here::here("output/plot.rds"))
plot
```









